\begin{thebibliography}{9}

\bibitem{rubenstein}
L.Z. Rupenstein,
{\em Falls in older people: epidemiology, risk factors and strategies for prevention},
Age and Aging 35 (suppl\_2) ii37-ii41,
\url{doi:10.1093/ageing/afl084},
\url{https://academic.oup.com/ageing/article/35/suppl_2/ii37/15775},
2006.

\bibitem{krupitzer}
C. Krupitzer, T. Sztyler, J. Edinger, M. Breitbach, H. Stuckenschmidt, C. Becker,
{\em Hips Do Lie! A Position-Aware Mobile Fall Detection System},
2018 IEEE International Conference of Pervasive Computing and Communication (PerCom),
pp. 1-10,
\url{doi:10.1109/PERCOM.2018.8444583},
2018.

\bibitem{gillespie}
L.D. Gillespie, M.C. Robertson, W.J. Gillespie, C. Sherrington, S.Gates, L.M. Clemson, S.E. Lamb,
{\em Interventions for preventing falls in older people living in the community},
Cochrane Database of Systematic Reviews (9),
\url{doi:10.1002/14651858.CD007146.pub3},
\url{https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD007146.pub3/abstract},
2009.

\bibitem{mancini}
M. Mancini, F.B. Horak,
{\em The relevance of clinical balance assessment tools to differentiate balance deficits},
European journal of physical and rehabilitation medicine 46 (2),
239-248,
\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3033730}
2010.

\bibitem{roeing}
K.L. Roeing, K.L. Hsieh, J.J. Sosnoff,
{\em A systematic review of balance and fall risk assessment with phone technology},
Archives of Gerontology and Geriatrics 73,
222-226,
\url{doi:10.1016/j.archger.2017.08.002},
\url{http://www.sciencedirect.com/science/article/pii/S0167494317302698}
2017.

\bibitem{fitzpatrick93}
Fitzpatrick, R., McCloskey, D.I.,
{\em The perception of sway during standing in humans},
J. Physiol.: 478, 173-176,
1993.

\bibitem{konradson96}
Konradson, L., Raun, J.B., Sorensen, A.J.,
{\em Proprioception at the ankle: the effect of anaesthetic blockade of ligament receptors},
J. Bone Joint Surg. Br: 75B, 433-436,
1993.

\bibitem{kavounoudias98}
Kavounoudias, A., Roll, R., Roll, J.P,
{\em The plantar sole is a 'dynamometric map' for human balance control},
NeuroReport: 9, 3247-3252,
1998.

\bibitem{wu97}
Wu, G., Chiang, H.J.,
{\em The significance of somatosensory stimulations to the human foot in the control of postural reflexes},
Exp Brain Res.: 114, 163-169,
1997.

\bibitem{sensors}
Flutter,
{\em Flutter plugin for accessing the Android and iOS accelerometer and gyroscope sensors},
v0.4.2,
\url{https://pub.dev/packages/sensors},
2020

\bibitem{cudropdown}
L. Calisti,
{\em A simple dropdown library with custom style},
v0.0.1,
\url{https://pub.dev/packages/custom_dropdown},
2020.

\bibitem{iirjdart}
L. Calisti,
{\em An IIR filter library written in Dart. Highpass, lowpass, bandpass and bandstop as Butterworth, Bessel and Chebyshev Type I/II},
v0.0.1,
\url{https://pub.dev/packages/iirjdart},
2020.

\bibitem{powerdart}
L. Calisti,
{\em Compute the Power Spectral Density (PSD) on Dart. This package runs everywhere dart runs},
v0.0.2,
\url{https://pub.dev/packages/powerdart},
2020.

\bibitem{abtdependencies}
L. Calisti,
{\em Automatically generate dart file with informations about used dependencies in pubspec.yaml},
v0.0.1,
\url{https://pub.dev/packages/about_dependencies},
2020.
\end{thebibliography}
